Syntactic realization with data-driven neural tree grammars

### 2016-10-11 paper/draft.tex
merigng

Table \ref{table:accresults} shows the results of supertag
prediction.
%
All differences between model are significant using a Paired-Sample t-test ($p<10^{-5}$)
%
The structural and atomic embedding methods consistently perform better,
suggesting that the clustering capabilities of neural methods is a
crucial part of their effectiveness.
%
For post-decoding performance, Fergus-N utilizes the structural embeddings more than the atomic embeddings. 
%Fergus-N seems to utilize the structural embeddings more, as its post-decoding performance is 
%The convolution encoding seems to work better with Fergus-N.  
%
This merits further investigation: it might be because Fergus-N
predicts one supertag as a function of another, and so the
compositional relationships among the two trees are more
important---or because Fergus-R's contextualized decisions depend on
similarities among supertags (involving argument structure or
information structure) that are difficult for the convolutional coding
to represent or learn.
%
Additionally, the minimal embeddings suggests that Fergus-N's architecture might provide enough structure to make some predictions greatly simplified. 
%Fergus-N's conditional supertag predictions might also account for the performance of the minimal encoding method and

@@

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
All differences in model are significant using an Independent\footnote{An Indepedent t-test was used instead of a Paired-Sample t-test because of intermittent failures during linearization that resulted in slightly different numbers of observations.} t-test ($p<10^{-5}$). 
%
For both models, the differences between structural embeddings (using convolutional coding) and atomic embeddings (using standard vector embedding techniques) were not significant, while the differences between the two embeddings and minimal embeddings were significant ($p<10^{-5}$). 
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of 16.7.
%
Our evaluation, on 2400 sentences with an average length of 22, is
more strenuous.

@@

The works most similar to ours explicitly model tree structures, but focus on resolving the uncertainty invovled with the latent structure of an observed sentence. 
%
For example, the top down tree structure of \newcite{zhang2016top} expresses the generation of a dependency structure as the decisions of a set of long short-term memory networks.  
%
For each decision, the possible options are different tree structures which can produce the target linear form.
%
In contrast, the generation problem is concerned with different linear forms that can result from the same tree structure. 
%
In more extensive tasks, the generation problem can include simulated interpretion to inform decisions; using the ease of structural inference from linear form quantifies the understandability of a sentence.

@@

\begin{table}[t!]
\centering
\begin{tabular}{lr}
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Fergus-N Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline
Batch size & 128 \\ \hline
\hline  \multicolumn{2}{|c|}{\textbf{Fergus-R Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline 
Hidden state size & 128 \\ \hline
Batch size & 16 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Embedding Parameters}} \\ \hline
Convolution filter size & 48 \\ \hline
Syntactic category embedding size & 32 \\ \hline
Node role embedding size & 32 \\ \hline
Word embedding size \newline
\cite{pennington2014glove} & 300 \\ \hline
\end{tabular}
&
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Language Model Parameters}} \\ \hline
Hidden state size & 368 \\ \hline
Batch size & 32 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Optimization Parameters}} \\ \hline
Optimization Algorithm & ADAM \\ \hline
Fergus-R and Fergus-N Learning Rate & 1e-4 \\ \hline
Language Model Learning Rate & 0.01 \\ \hline
Fully-Connected Dropout Rate & 0.5 \\ \hline
Recurrent Weight Dropout Rate & 0.2 \\ \hline
$L_2$ Weight Decay & 1e-6 \\ \hline
Max gradient norm & 10.0 \\ \hline
Gradient clip threshold & 5.0 \\ \hline
\end{tabular}
\end{tabular}
\caption{The parameters for the Fergus-R, Fergus-N, and language models.  The
exact specifications in configuration files can be found in the code repository that accompanies this paper.}
\label{tab:params}
%\vspace*{-0.5cm}
\end{table}

@@

In our experiments, the corpus was preprocessed using the Stanford
Parser to fix common issues and remove extraneous information.  The
resulting parse trees were then analyzed to mark the head words, the
dependents, and the adjuncts.  The marked-up trees were split at
adjunction and substitution positions to form the grammar.  Our models
use an output distribution that's restricted to the set of supertags
that have occurred with the lexical item, which requires indices to
the supertag embedding matrix to be passed into the computation with
the rest of the data.  We implement the affinity matrix between the
supertag embeddings and lexical state vectors, by concatenating the
vectors, mapping them to a new space using a fully connected layer,
and computing a score with a vectorized function.
%
(The vectorized function operation is the same mechanism which
calculates the probability distribution used in soft attention.)

>>>>

Table \ref{table:accresults} shows the results of supertag
prediction.
%
All differences between model are significant using a Paired-Sample t-test ($p<10^{-5}$)
%
The structural and atomic embedding methods consistently perform better,
suggesting that the clustering capabilities of neural methods is a
crucial part of their effectiveness.
%
For post-decoding performance, Fergus-N utilizes the structural embeddings more than the atomic embeddings. 
%Fergus-N seems to utilize the structural embeddings more, as its post-decoding performance is 
%The convolution encoding seems to work better with Fergus-N.  
%
This merits further investigation: it might be because Fergus-N
predicts one supertag as a function of another, and so the
compositional relationships among the two trees are more
important---or because Fergus-R's contextualized decisions depend on
similarities among supertags (involving argument structure or
information structure) that are difficult for the convolutional coding
to represent or learn.
%
Additionally, the minimal embeddings suggests that Fergus-N's architecture might provide enough structure to reduce the difficulty of a large number of cases. 
%Fergus-N's conditional supertag predictions might also account for the performance of the minimal encoding method and

@@

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
All differences in model are significant using an Independent t-test ($p<10^{-5}$).  \footnote{An Indepedent t-test was used instead of a Paired-Sample t-test because of intermittent failures during linearization that resulted in slightly different numbers of observations.}
%
For both models, the differences between structural embeddings (using convolutional coding) and atomic embeddings (using standard vector embedding techniques) were not significant, while the differences between the two embeddings and minimal embeddings were significant ($p<10^{-5}$). 
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of 16.7.
%
Our evaluation, on 2400 sentences with an average length of 22.1, is
more strenuous.

@@

The works most similar to ours explicitly model tree structures, but focus on resolving the uncertainty involved with the latent structure of an observed sentence. 
%
For example, the top down tree structure of \newcite{zhang2016top} expresses the generation of a dependency structure as the decisions of a set of long short-term memory networks.  
%
For each decision, the possible options are different tree structures which can produce the target linear form.
%
In contrast, the generation problem is concerned with different linear forms that can result from the same tree structure. 
%
In more extensive tasks, the generation problem can include simulated interpretion to inform decisions; using the ease of structural inference from linear form quantifies the understandability of a sentence.

@@

\begin{table}[b!]
\vspace{-0.1cm}
\centering
\begin{tabular}{lr}
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Fergus-N Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline
Batch size & 128 \\ \hline
\hline  \multicolumn{2}{|c|}{\textbf{Fergus-R Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline 
Hidden state size & 128 \\ \hline
Batch size & 16 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Embedding Parameters}} \\ \hline
Convolution filter size & 48 \\ \hline
Syntactic category embedding size & 32 \\ \hline
Node role embedding size & 32 \\ \hline
Word embedding size \newline
\cite{pennington2014glove} & 300 \\ \hline
\end{tabular}
&
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Language Model Parameters}} \\ \hline
Hidden state size & 368 \\ \hline
Batch size & 32 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Optimization Parameters}} \\ \hline
Optimization Algorithm & ADAM \\ \hline
Fergus-R and Fergus-N Learning Rate & 1e-4 \\ \hline
Language Model Learning Rate & 0.01 \\ \hline
Fully-Connected Dropout Rate & 0.5 \\ \hline
Recurrent Weight Dropout Rate & 0.2 \\ \hline
$L_2$ Weight Decay & 1e-6 \\ \hline
Max gradient norm & 10.0 \\ \hline
Gradient clip threshold & 5.0 \\ \hline
\end{tabular}
\end{tabular}
\caption{The parameters for the Fergus-R, Fergus-N, and language models.  The
exact specifications in configuration files can be found in the code repository that accompanies this paper.}
\label{tab:params}
%\vspace*{-0.5cm}
\end{table}

@@

In our experiments, the corpus was preprocessed using Stanford NLP tools \cite{de2006generating} to fix common issues and remove extraneous information.  The
resulting parse trees were then analyzed to mark the head words, the
dependents, and the adjuncts.  The marked-up trees were split at
adjunction and substitution positions to form the grammar.  Our models
use an output distribution that's restricted to the set of supertags
that have occurred with the lexical item, which requires indices to
the supertag embedding matrix to be passed into the computation with
the rest of the data.  We implement the affinity matrix between the
supertag embeddings and lexical state vectors, by concatenating the
vectors, mapping them to a new space using a fully connected layer,
and computing a score with a vectorized function.
%
(The vectorized function operation is the same mechanism which
calculates the probability distribution used in soft attention.)
